\clearpage
\section*{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begin{enumerate}[leftmargin=1cm,label=\arabic*.]
\item Sutton R.\,S., Barto A.\,G. Reinforcement Learning: An Introduction. 2nd ed. Cambridge: MIT Press, 2018. 552 p.
\item Hyndman R.\,J., Athanasopoulos G. Forecasting: Principles and Practice. 3rd ed. Melbourne: OTexts, 2021. 442 p.
\item Tsay R.\,S. Analysis of Financial Time Series. 3rd ed. Hoboken: Wiley, 2010. 720 p.
\item Box G.\,E.\,P., Jenkins G.\,M., Reinsel G.\,C., Ljung G.\,M. Time Series Analysis: Forecasting and Control. 5th ed. Hoboken: Wiley, 2015. 712 p.
\item Murphy J.\,J. Technical Analysis of the Financial Markets. New York: New York Institute of Finance, 1999. 576 p.
\item Chan E.\,P. Algorithmic Trading: Winning Strategies and Their Rationale. Hoboken: Wiley, 2013. 224 p.
\item López de Prado M. Advances in Financial Machine Learning. Hoboken: Wiley, 2018. 400 p.
\item Mnih V., Kavukcuoglu K., Silver D. et al. Human-level Control through Deep Reinforcement Learning // Nature. 2015. Vol. 518. P. 529--533.
\item Schulman J., Wolski F., Dhariwal P., Radford A., Klimov O. Proximal Policy Optimization Algorithms // arXiv preprint arXiv:1707.06347. 2017.
\item Mnih V., Badia A.\,P., Mirza M. et al. Asynchronous Methods for Deep Reinforcement Learning // Proceedings of the 33rd International Conference on Machine Learning. 2016. P. 1928--1937.
\item Hochreiter S., Schmidhuber J. Long Short-Term Memory // Neural Computation. 1997. Vol. 9, No. 8. P. 1735--1780.
\item Cho K., Van Merriënboer B., Gulcehre C. et al. Learning Phrase Representations using RNN Encoder--Decoder for Statistical Machine Translation // arXiv preprint arXiv:1406.1078. 2014.
\item Breiman L. Random Forests // Machine Learning. 2001. Vol. 45. P. 5--32.
\item Friedman J.\,H. Greedy Function Approximation: A Gradient Boosting Machine // The Annals of Statistics. 2001. Vol. 29, No. 5. P. 1189--1232.
\item Pedregosa F., Varoquaux G., Gramfort A. et al. Scikit-learn: Machine Learning in Python // Journal of Machine Learning Research. 2011. Vol. 12. P. 2825--2830.
\item Harris C.\,R., Millman K.\,J., van der Walt S.\,J. et al. Array Programming with NumPy // Nature. 2020. Vol. 585. P. 357--362.
\item McKinney W. Data Structures for Statistical Computing in Python // Proceedings of the 9th Python in Science Conference. 2010. P. 56--61.
\item Paszke A., Gross S., Massa F. et al. PyTorch: An Imperative Style, High-Performance Deep Learning Library // Advances in Neural Information Processing Systems. 2019. Vol. 32. P. 8024--8035.
\item Raffin A., Hill A., Gleave A., Kanervisto A., Ernestus M., Dormann N. Stable-Baselines3: Reliable Reinforcement Learning Implementations // Journal of Machine Learning Research. 2021. Vol. 22. P. 1--8.
\item Towers M., Terry J.\,K., Kwiatkowski A. et al. Gymnasium // GitHub repository. URL: https://gymnasium.farama.org/ (дата обращения: 28.04.2026).
\item Yang H., Liu X.-Y., Zhong S., Walid A. FinRL: A Deep Reinforcement Learning Library for Automated Stock Trading in Quantitative Finance // NeurIPS 2020 Workshop on Financial Technology and FinRL. 2020.
\item The TensorTrade Authors. TensorTrade Documentation. URL: https://tensortrade-ng.io/ (дата обращения: 28.04.2026).
\item AminHP. gym-anytrading Documentation. URL: https://github.com/AminHP/gym-anytrading (дата обращения: 28.04.2026).
\item Yahoo Finance API via yfinance Documentation. URL: https://github.com/ranaroussi/yfinance (дата обращения: 28.04.2026).
\item Fama E.\,F. Efficient Capital Markets: A Review of Theory and Empirical Work // The Journal of Finance. 1970. Vol. 25, No. 2. P. 383--417.
\item Lo A.\,W., MacKinlay A.\,C. A Non-Random Walk Down Wall Street. Princeton: Princeton University Press, 1999. 288 p.
\item Bailey D., López de Prado M. The Sharpe Ratio Efficient Frontier // Journal of Risk. 2012. Vol. 15, No. 2. P. 3--44.
\item Magdon-Ismail M., Atiya A.\,F. Maximum Drawdown // Risk Magazine. 2004. Vol. 17, No. 10. P. 99--102.
\end{enumerate}
